Usage metrics

### 2021-03-09 analysis/usage.Rmd
Prefix plot pdf by the dataset name

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

ggsave(path(PLOT_DIR, "eval_calls_per_packages.pdf"))
```

@@

ggsave(path(PLOT_DIR, "size_loaded_distribution.pdf"))
```

@@

ggsave(path(PLOT_DIR, "events_per_pack_large.pdf"))
```

@@

ggsave(path(PLOT_DIR, "events_per_pack_small.pdf"))
```

@@

ggsave(path(PLOT_DIR, "calls_per_run_per_call_site.pdf"))
```

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/base/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

ggsave_prefix("eval_calls_per_packages.pdf")
```

@@

ggsave_prefix("size_loaded_distribution.pdf")
```

@@

ggsave_prefix("events_per_pack_large.pdf")
```

@@

ggsave_prefix("events_per_pack_small.pdf")
```

@@

ggsave_prefix("calls_per_run_per_call_site.pdf")
```
